\documentclass{mipt-thesis-bs}
% Следующие две строки нужны только для biblatex. Для inline-библиографии их следует убрать.
\usepackage{mipt-thesis-biblatex}
\usepackage{amsmath}
\usepackage[nottoc,notlot,notlof]{tocbibind}
\usepackage{tocloft}
\usepackage[backend=biber]{biblatex} 
\usepackage{graphicx}
\usepackage{hyperref}
		
%Some customization of hyperref	
		
\addbibresource{main.bib}

\title{Применение методов машинного обучения в задаче радиометрической классификации}
\author{Кайдаш А.\,А.}
\supervisor{Дворкович А.\,В.}
%\referee{Петров Д.\,Е.}       % требуется только для mipt-thesis-ms
\groupnum{Б01-813б}
\faculty{Физтех-школа Радиотехники и Компьютерных Технологий}
\department{Кафедра мультимедийных технологий и телекоммуникаций}

\begin{document}

\frontmatter
\titlecontents
\mainmatter

%\input{chapters/abbreviations}

\input{chapters/0intro}
\input{chapters/1obzor}
\input{chapters/2methods}
\input{chapters/3def}
\input{chapters/4research}
\input{chapters/5summary}

\backmatter
\begin{thebibliography}{99}
    
    \bibitem{0}
        Merchant, K., Revay, S., Stantchev, G., et al.: \\Deep learning for RF device fingerprinting in cognitive communication networks. \\\emph{IEEE J. Sel. Top. Signal Process.}, 12(1), 160–167 (2018)
    \bibitem{2}   
        Danev, B., Capkun, S.: \\Transient-based identification of wireless sensor nodes. \\\emph{ International Conference on Information Processing in Sensor Networks IEEE 2009}, pp. 25–36. IEEE (2009)
    \bibitem{5}   
        Toonstra, J., Kinsner, W.: \\Transient analysis and genetic algorithms for classification. \\\emph{ Conference Proceedings of the IEEE Communications, Power, and Computing IEEE 1995}, WESCANEX 95, vol. 2, pp. 432–437. IEEE (1995)
    \bibitem{7}    
        Polak, A.C., Dolatshahi, S., Goeckel, D.L.: \\Identifying wireless users via transmitter imperfections. \\\emph{IEEE J. Sel. Areas Commun.} 29(7), 1469–1479 (2011)
    \bibitem{16}
        Novikoff A. B. J. :\\
        On convergence proofs on perceptrons \\
        \emph{Proceedings of the Symposium on the Mathematical Theory of Automata.} \\
         Vol. 12.  Polytechnic Institute of Brooklyn, 1962.  Pp. 615–622
    \bibitem{13}
        Nigmatullin R.R., Vorobev A.S.: \\The “Universal” Set of Quantitative Parameters for Reading of the Trendless Sequences\\  \emph{ Fluctuation and Noise Letters}, 18(04), 2019
    \bibitem{3}   
        Li, Z., Xu, W., Miller, R., et al.: \\Securing wireless systems via lower layer enforcements. \\\emph{ ACM Workshop on Wireless Security ACM}, pp. 33–42. ACM (2006)
    \bibitem{8}    
        К. В. Воронцов \\Математические методы обучения по прецедентам
(теория обучения машин), \\\emph{В рамках курса лекций по машинному обучению,} 2013
    \bibitem{9}    
        Nguyen, N.T., Zheng, G., Han, Z., et al.: \\Device fingerprinting to enhance wireless security using nonparametric Bayesian method. \\\emph{ Proceedings IEEE, INFOCOM 2011, IEEE 2011}, vol. 34, pp. 1404–1412. IEEE (2011)
     \bibitem{11}
        A. Selcuk Uluagac, Sakthi V. Radhakrishnan, Cherita Corbett, Antony Baca, Raheem Beyah:\\ A passive technique for fingerprinting wireless devices with Wired-side Observations.\\ \emph{Conference on Communications and Network Security (CNS)} 2013 IEEE
    \bibitem{6}    
        Gao, K., Corbett, C., Beyah, R.: \\A passive approach to wireless device fingerprinting. \\\emph{ IEEE/IFIP International Conference on Dependable Systems and Networks}, IEEE 2010, pp. 383–392. IEEE (2010)
    \bibitem{12}
        Marco Tulio Ribeiro, Sameer Singh, and Carlos Guestrin:  \\"Why Should I Trust You?": Explaining the Predictions of Any Classifier. \\ \emph{ In Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining (KDD '16). Association for Computing Machinery}, New York, NY, USA, 1135–1144. 2016.
    \bibitem{4}   
        Liang, X., Greenstein, L., Mandayam, N., et al.: \\Fingerprints in the ether: using the physical layer for wireless authentication. \\\emph{ IEEE International Conference on Communications IEEE}, pp. 4646–4651. IEEE (2009)
    \bibitem{14}
        Minsky M., Papert S.:\\
        Perceptrons: an Introduction to Computational Geometry. \\
        \emph{MIT Press}, 1968.
    \bibitem{15}
        LeCun Y., Denker J., Solla S., Howard R. E., Jackel L. D.:\\
        Optimal brain damage \\
        \emph{Advances in Neural Information Processing Systems II} \\
        Ed. by D. S. Touretzky. \\
        San Mateo, CA: Morgan Kauffman, 1990.
    \bibitem{1}
        Polak, A.C., Goeckel, D.L.: \\Wireless device identification based on RF oscillator imperfections. \\\emph{ IEEE International Conference on Acoustics, Speech and Signal Processing IEEE}, vol. 10, pp. 2492–2501. IEEE (2014)
    \end{thebibliography}
\end{document}